Explore the SingleR results

### 2025-07-24 analyses/cell-type-neuroblastoma-04/exploratory-notebooks/singler-results.Rmd
add brief section looking at smaller libraries

heatmap_col_fun <- circlize::colorRamp2(c(0, 1), colors = c("white", "darkslateblue"))

@@

>>>>

@@

## Inferences from libraries with lower cell counts

In this section, we briefly look at annotation results for libraries with fewer than 1000 cells which may be lower quality than other libraries.

Those libraries are:

```{r}
libraries_low_cells <- celltype_recoded_df |>
  dplyr::filter(annotation_type == "singler") |>
  dplyr::select(-annotation_type) |>
  dplyr::count(library_id, name = "total_cells") |>
  dplyr::filter(total_cells < 1000) 
libraries_low_cells
```

### Heatmap

This section shows a heatmap comparing annotations from these libraries only to the consensus annotations.

```{r, fig.width = 8, fig.height = 8}
make_jaccard_heatmap(
  celltype_recoded_wide_df |> dplyr::filter(library_id %in% libraries_low_cells$library_id),
  "consensus_validation",
  "singler",
  "Consensus validation label",
  "SingleR NBAtlas label"
)
```

The heatmap comparison to consensus cell types for these libraries looks reasonable; corresponding cell types tend to match up.
Note that because this heatmap includes fewer libraries, there are fewer cell types to display overall.

### Percent of unclassified cells

Next, we'll ask whether the percent of unclassified cells (aka, `unknown_singler`) is much higher in these libraries compared to larger libraries.

```{r}
unknown_singler_df <- celltype_recoded_wide_df |>
  dplyr::group_by(library_id) |>
  dplyr::summarize(unknown_cells= sum(singler == "unknown_singler"))

celltype_recoded_wide_df |>
  dplyr::add_count(library_id, name = "total_cells") |>
  dplyr::inner_join(unknown_singler_df, by = "library_id") |>
  dplyr::select(library_id, total_cells, unknown_cells) |>
  dplyr::distinct() |>
  dplyr::mutate(percent_singler_unclassified = round(unknown_cells/total_cells, 2)) |>
  dplyr::arrange(total_cells)
```

Most cells in the relatively smaller libraries are classified, and the percentage of unclassified cells (when non-0) is fully in line with the larger libraries.
